---
title: "Final Project"
author: "Wani Qiu"
date: '2022-12-11'
output:
  pdf_document: default
  html_document: default
---

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(simstudy)
library(dplyr)
library(here)  # makes reading data more consistent
library(tidyverse)  # for data manipulation and plotting
library(haven)  # for importing SPSS/SAS/Stata data
library(lme4)  # for multilevel analysis
library(lmerTest)  # for testing coefficients
library(MuMIn)  # for R^2
library(sjPlot)  # for plotting effects
library(emmeans)  # for marginal means
library(modelsummary)  # for making tables
library(readxl)
library(sjmisc)
library(brms)
library(sjlabelled)
library(insight)
```

#### Research Questions

1. Does the truth value of the information predict children's transmission of interesting information?

2. Does the interestingness of the information predict children's transmission of true information?

### Load data
```{r}
dat <- read_xlsx(here("Flashy Coding Sheet exp 2.xlsx")) 

table(dat$age, dat$intrue)
table(dat$age, dat$trueres)

dat%>%
  group_by(age, intrue)%>%
  count(trueres)
dat%>%
  group_by(age, intrue)%>%
  count(inres)
dat%>%
  group_by(age)%>%
  count()

dat$intrue <- as.factor(dat$intrue)
dat$inres <- as.factor(dat$inres)
dat$trueres <- as.factor(dat$trueres)
dat$age <- as.factor(dat$age)
```

Where intrue = 0 is when the interesting fact is false (and thus the neutral fact true), and intrue = 1 is when the interesting fact is true (and thus the neutral fact false)


## RS1. Are children's preferences to teach sensational information predicted by the truth value of the information?

### Test random slopes
```{r}
m <- glmer(intrue~ (1|subject), data = dat, family = binomial("logit"))
summary(m)

# item-level variable, such as intrue, have no person-level variance
```

```{r}
#visualize person-level and item-level variance
set.seed(112)
# Variation across persons
random_ids <- sample(unique(dat$subject), size = 10)
dat %>%
    filter(subject %in% random_ids) %>%  # select only 10 participants
    ggplot(aes(x = factor(subject), y = inres)) +
    geom_jitter(height = 0.5, width = 0.1, alpha = 0.3) +
    # Add person means
    stat_summary(fun = "mean", geom = "point", col = "red",
      shape = 17,  # use triangles
      size = 2  # make them larger
    ) +
    # change axis labels
    labs(x = "Person ID", y = "fact selection")

# Variation across items
random_items <- sample(unique(dat$item), size = 10)
dat %>%
    filter(item %in% random_items) %>%  # select only 10 participants
    ggplot(aes(x = factor(item), y = inres)) +
    geom_jitter(height = 0.5, width = 0.1, alpha = 0.3) +
    # Add person means
    stat_summary(fun = "mean", geom = "point", col = "red",
      shape = 17,  # use triangles
      size = 2  # make them larger
    ) +
    # change axis labels
    labs(x = "Item Number", y = "fact selection")
```

```{r message=FALSE, warning=FALSE, results='hide'}
#brms
#ICC
m_ri1 <- brm(inres ~ intrue * age + (1 | subject) + (1 | item),
           data = dat, family = bernoulli("logit"),
           prior = prior(student_t(3, 0, 1), class = "b"),
           seed = 144)
```

```{r}
summary(m_ri1)
tot <- 0.85^2 + 0.55^2+(pi^2/3) #total variance
subject <- (0.55^2)/tot
item <- (0.85^2)/tot
tot #total variance is 4.38
subject #.070
item #.167
```

Total variance is 4.38. Variability at the subject level accounts for 7% of the total variability in responses. Variability at the item level accounts for for 17% of the total variability in responses. We will need to include random intercepts as there is evidence that there is variation across participants and items.

```{r message=FALSE, warning=FALSE, results='hide'}
m_brm <- brm(inres ~ intrue * age + (1 | subject) + (age | item),
           data = dat, family = bernoulli("logit"),
           prior = prior(student_t(3, 0, 1), class = "b"),
           seed = 144)
```

```{r}
summary(m_brm)

loo(m_ri1, m_brm) #since the looic for m_ri1 is smaller, age will not be included as a random slope at the item level
```

```{r message=FALSE, warning=FALSE, results='hide'}
m_brm1 <- brm(inres ~ intrue * age + (intrue | subject) + (1 | item),
           data = dat, family = bernoulli("logit"),
           prior = prior(student_t(3, 0, 1), class = "b"),
           seed = 144)
```

```{r}

loo(m_ri1, m_brm1) #since m_ri1 has a smaller looic value (179.8) compared to m_brm1(181), we do not need to include random slopes for intrue.
```

```{r message=FALSE, warning=FALSE, results='hide'}
m_brm2 <- brm(inres ~ intrue * age + (intrue | subject) + (age + intrue| item),
           data = dat, family = bernoulli("logit"),
           prior = prior(student_t(3, 0, 1), class = "b"),
           seed = 144)
```

```{r}
loo(m_ri1, m_brm2) #since m_ri1 has a smaller looic value, we do not need to include random slopes for intrue or age at the item level.
```

```{r message=FALSE, warning=FALSE, results='hide'}

#final model with prior set on interaction term only
fin_model <- brm(inres ~ intrue * age + (1 | subject) + (1 | item),
           data = dat, family = bernoulli("logit"),
           prior = prior(student_t(3, 0, 1), class = "b", coef = "intrue1:age5"),
           seed = 144)

#final model with prior set on all terms
fin_model1 <- brm(inres ~ intrue * age + (1 | subject) + (1 | item),
           data = dat, family = bernoulli("logit"),
           prior = prior(student_t(3, 0, 1), class = "b"),
           seed = 144)
```

```{r}
tab_model(fin_model, fin_model1)
summary(fin_model)
summary(fin_model1)
#effect size
performance::r2(fin_model)
```

The results are mostly comparable for the two models (one with the prior set on the interaction term only, and one with the prior set on all terms). We will use the model with the prior set on all terms as our final model.

### Plot for Research Question 1

```{r}
bayes_m1 <- conditional_effects(fin_model)
plot <- plot(bayes_m1, plot = FALSE)[[3]] +
  labs(x = "Interesting X Truth Condition",
       y = "Probability of Teaching Interesting Information")+
  scale_x_discrete("Truth Value",
  labels = c("0" = "False", 
             "1" = "True"))
plot
```

## RS2. Are children's decisions to teach true information predicted by the interestingness of the information?

```{r message=FALSE, warning=FALSE, results='hide'}
#ICC
m_ri2 <- brm(trueres ~ intrue * age + (1 | subject) + (1 | item),
           data = dat, family = bernoulli("logit"),
           prior = prior(student_t(3, 0, 1), class = "b"),
           seed = 144)
```

```{r}
summary(m_ri2)
tot <- 0.98^2 + 0.36^2+(pi^2/3) #total variance
subject <- (0.98^2)/tot
item <- (0.36^2)/tot
tot #total variance is 4.38
subject #variability at the subject level accounts for 22% of the total variability in responses
item #variability at the item level accounts for for 3% of the total variability in responses
```
We will need to include random intercepts for subject only.

```{r message=FALSE, warning=FALSE, results='hide'}
#brms with intrue as random slope
m_brm3 <- brm(trueres ~ intrue * age + (intrue | subject),
           data = dat, family = bernoulli("logit"),
           prior = prior(student_t(3, 0, 1), class = "b"),
           seed = 144)
```

```{r}
loo(m_ri2, m_brm3)

#no need to include intrue as random slopes for subject
```

```{r message=FALSE, warning=FALSE, results='hide'}
#brms with no random slopes
m_brm4 <- brm(trueres ~ intrue * age + (1 | subject),
           data = dat, family = bernoulli("logit"),
           prior = prior(student_t(3, 0, 1), class = "b"),
           seed = 144)
```

```{r}
loo(m_ri2, m_brm4) #m_brm4 will be our final model with the lowest looic value of 174.3
```


```{r message=FALSE, warning=FALSE, results='hide'}
#compare model with prior set on all terms vs. prior set only on interaction term
m_brm5 <- brm(trueres ~ intrue * age + (1 | subject),
           data = dat, family = bernoulli("logit"),
           prior = prior(student_t(3, 0, 1), class = "b", coef = "intrue1:age5"),
           seed = 144)
```

```{r}
tab_model(m_brm4, m_brm5)
summary(m_brm4)
summary(m_brm5)
```

The model with the prior set only on the interaction term yielded a smaller odds ratio for the interaction between intrue and age, and larger main effect for age. The standard error for the model with the prior set only on the interaction term had a larger standard error on average. 

```{r message=FALSE, warning=FALSE}
bayes_m2 <- conditional_effects(m_brm4)
plot2 <- plot(bayes_m2, plot = FALSE)[[3]] +
  labs(x = "Interesting X Truth Condition",
       y = "Probability of Teaching True Information")+
  scale_x_discrete("Interestingness Value",
  labels = c("0" = "Neutral", 
             "1" = "Interesting"))
plot2

tab_model(fin_model, m_brm4)
```


